Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
Change wordings and use brakets

\begin{definition}
	Let $|\widehat{t}\rangle=|11\ldots1\rangle |00\ldots0\rangle$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
\end{definition}

@@

\subsection{Reduction to Real Quantum Computation}

@@

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.

First, we rewrite the circuit to consist of only controlled phase gates and 1-qubit gates. TODO: prove that these 1-qubit gates are all real. We ensure that each $C_\phi$s are preceded and followed by two $Z$ gates. That is, if the $C_\phi$ acts on the qubits $f_t$ and $s_t$, then the circuit would look like $Z_{f_t}Z_{s_t}C_\phi Z_{s_t}Z_{f_t}$ around each $C_\phi$. We then pad the circuit so that the $C_\phi$s are applied at $t\in T_2=\{L, 2L, 3L, \ldots\}$ for some $L\in\mathbb{N}$. Let $T_1=[T]\setminus T_2$ be time steps corresponding to 1-qubit gates.

\subsection{Constructing the 2-local Hamiltonian instance}

We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1|x\rangle\otimes|\hat{t}\rangle$$. We do so by causing states perpendicular to this to have high eigenvalues.

First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes |01\rangle\langle01|_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
We note that when stricted to $S_{legal}$, 
\begin{itemize}
	\item $|10\rangle\langle10|_{t,t+1}
		=|\widehat{t}\rangle\langle\widehat{t}|$ 
	\item $|1\rangle\langle0|_{t+1}
		=|\widehat{t+1}\rangle\langle\widehat{t}|$
	\item $|11\rangle\langle00|_{t,t+1}
		=|\widehat{t+2}\rangle\langle\widehat{t}|$
\end{itemize}

Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
	$$H_{prop,t}=I\otimes|\widehat{t}\rangle\langle\widehat{t}|
		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
		-U_t\otimes|\widehat{t}\rangle\langle\widehat{t-1}|
		-U_t^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$

@@

Let $S_{prop1}=\ker H_{prop1}$.
Then, $S_{prop1}$ has the following as basis:
\begin{itemize}
	\item $|00\rangle_{f_t,s_t}|\xi_{00}\rangle\otimes
		(|\widehat{t}\rangle+|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
	\item $|01\rangle_{f_t,s_t}|\xi_{01}\rangle\otimes
		(|\widehat{t}\rangle+|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
	\item $|10\rangle_{f_t,s_t}|\xi_{10}\rangle\otimes
		(|\widehat{t}\rangle-|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)$
	\item $|11\rangle_{f_t,s_t}|\xi_{11}\rangle\otimes
		(|\widehat{t}\rangle-|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)$
\end{itemize}

Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
\begin{itemize}
	\item $|0\rangle\langle0|_{f_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle+|\widehat{t+1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t+1}|)$
	\item $|1\rangle\langle1|_{f_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle-|\widehat{t+1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t+1}|)$
	\item $|0\rangle\langle0|_{s_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t+1}\rangle+|\widehat{t+2}\rangle)
		(\langle\widehat{t+1}|+\langle\widehat{t+2}|)$
	\item $|1\rangle\langle1|_{s_t}\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t+1}\rangle-|\widehat{t+2}\rangle)
		(\langle\widehat{t+1}|-\langle\widehat{t+2}|)$
	\item $(|00\rangle\langle00|_{f_t,s_t}
		+|11\rangle\langle11|_{f_t,s_t})\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle+|\widehat{t+2}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t+2}|)$
	\item $(|01\rangle\langle01|_{f_t,s_t}
		+|10\rangle\langle10|_{f_t,s_t})\otimes
		|\widehat{t}\rangle\langle\widehat{t}|
		=(|\widehat{t}\rangle-|\widehat{t+2}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t+2}|)$
\end{itemize}

Similarly,
\begin{itemize}
	\item $|0\rangle\langle0|_{f_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle+|\widehat{t-2}\rangle)
		(\langle\widehat{t-1}|+\langle\widehat{t-2}|)$
	\item $|1\rangle\langle1|_{f_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle-|\widehat{t-2}\rangle)
		(\langle\widehat{t-1}|-\langle\widehat{t-2}|)$
	\item $|0\rangle\langle0|_{s_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-2}\rangle+|\widehat{t-3}\rangle)
		(\langle\widehat{t-2}|+\langle\widehat{t-3}|)$
	\item $|1\rangle\langle1|_{s_t}\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-2}\rangle-|\widehat{t-3}\rangle)
		(\langle\widehat{t-2}|-\langle\widehat{t-3}|)$
	\item $(|00\rangle\langle00|_{f_t,s_t}
		+|11\rangle\langle11|_{f_t,s_t})\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle+|\widehat{t-3}\rangle)
		(\langle\widehat{t-1}|+\langle\widehat{t-3}|)$
	\item $(|01\rangle\langle01|_{f_t,s_t}
		+|10\rangle\langle10|_{f_t,s_t})\otimes
		|\widehat{t-1}\rangle\langle\widehat{t-1}|
		=(|\widehat{t-1}\rangle-|\widehat{t-3}\rangle)
		(\langle\widehat{t-1}|-\langle\widehat{t-3}|)$
\end{itemize}

Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
	$$H_t=I\otimes|\widehat t\rangle\langle\widehat t|
		+I\otimes|\widehat{t-1}\rangle\langle\widehat{t-1}|
		-C_\phi\otimes|\widehat t\rangle\langle\widehat{t-1}|
		-C_\phi^\dagger\otimes|\widehat{t-1}\rangle\langle\widehat{t}|$$
	$$H'=\sum_{t\in T_2}H_t$$
	Equivalently, $H_t=$

	$|00\rangle\langle00|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|01\rangle\langle01|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|10\rangle\langle10|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|11\rangle\langle11|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t-1}|)$

@@

	$|00\rangle\langle00|_{f_t,s_t}\otimes
		4(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|01\rangle\langle01|_{f_t,s_t}\otimes
		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|10\rangle\langle10|_{f_t,s_t}\otimes
		2(|\widehat{t}\rangle-|\widehat{t-1}\rangle)
		(\langle\widehat{t}|-\langle\widehat{t-1}|)+$

	$|11\rangle\langle11|_{f_t,s_t}\otimes
		(|\widehat{t}\rangle+|\widehat{t-1}\rangle)
		(\langle\widehat{t}|+\langle\widehat{t-1}|)$
instead.

@@

	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
	$$(-2|0\rangle\langle0|_{f_t}-2|0\rangle\langle0|_{s_t}
		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t})\otimes$$
	$$(|\widehat{t}\rangle\langle\widehat{t-1}|+
		|\widehat{t-1}\rangle\langle\widehat{t}|)+$$
	$$(2|0\rangle\langle0|_{f_t}+2|0\rangle\langle0|_{s_t}
		+|1\rangle\langle1|_{f_t}+|1\rangle\langle1|_{s_t}
		-2|01\rangle\langle01|_{f_t,s_t}
		-2|10\rangle\langle10|_{f_t,s_t})\otimes$$
	$$(|\widehat{t-1}\rangle\langle\widehat{t-1}|+
		|\widehat{t}\rangle\langle\widehat{t}|)$$

Lastly, we check if the input is right...
	$$H_{in}=\sum_{i=m+1}^N|1\rangle\langle1|_i\otimes|0\rangle\langle0|$$

>>>>

\begin{definition}
	Let $\ket{\widehat{t}}=\ket{11\ldots1} \ket{00\ldots0}$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
\end{definition}

@@

@@

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$

We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end. This is so that the final output has a higher chance to be measured in the final result in the following reduction.

After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.

\subsection{Constructing a local Hamiltonian instance}

We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$. We do so by ensuring states perpendicular to it have high eigenvalues.

First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
We note that when stricted to $S_{legal}$, 
\begin{itemize}
	\item $\ket{10}\bra{10}_{t,t+1}
		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
	\item $\ket{1}\bra{0}_{t+1}
		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
	\item $\ket{11}\bra{00}_{t,t+1}
		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
\end{itemize}

Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

@@

Let $S_{prop1}=\ker H_{prop1}$.
Then, $S_{prop1}$ has the following as basis:
\begin{itemize}
	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
\end{itemize}

Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
\begin{itemize}
	\item $\ket{0}\bra{0}_{f_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
	\item $\ket{1}\bra{1}_{f_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
	\item $\ket{0}\bra{0}_{s_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
	\item $\ket{1}\bra{1}_{s_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
	\item $(\ket{00}\bra{00}_{f_t,s_t}
		+\ket{11}\bra{11}_{f_t,s_t})\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
	\item $(\ket{01}\bra{01}_{f_t,s_t}
		+\ket{10}\bra{10}_{f_t,s_t})\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
\end{itemize}

Similarly,
\begin{itemize}
	\item $\ket{0}\bra{0}_{f_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
	\item $\ket{1}\bra{1}_{f_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
	\item $\ket{0}\bra{0}_{s_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
	\item $\ket{1}\bra{1}_{s_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
	\item $(\ket{00}\bra{00}_{f_t,s_t}
		+\ket{11}\bra{11}_{f_t,s_t})\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
	\item $(\ket{01}\bra{01}_{f_t,s_t}
		+\ket{10}\bra{10}_{f_t,s_t})\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
\end{itemize}

Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
	$$H'=\sum_{t\in T_2}H_t$$
	Equivalently, $H_t=$

	$\ket{00}\bra{00}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{01}\bra{01}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{10}\bra{10}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{11}\bra{11}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$

@@

	$\ket{00}\bra{00}_{f_t,s_t}\otimes
		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{01}\bra{01}_{f_t,s_t}\otimes
		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{10}\bra{10}_{f_t,s_t}\otimes
		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{11}\bra{11}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
instead.

@@

	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
		-2\ket{01}\bra{01}_{f_t,s_t}
		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
		\ket{\widehat{t}}\bra{\widehat{t}})$$

Lastly, we check if the input is right...
	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$
